### 2021-04-28 paper/output/document/paper31.tex
added kroy and prettified

%
\begin{isabellebody}%
\setisabellecontext{paper{\isadigit{3}}{\isadigit{1}}}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{The Categorical Imperative%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
In this section, I will present three formulations of the categorical imperative. In Section 3.1, I will 
consider a simple, naive formulation of the formula of universal law. This formulation is, as I will 
show, clearly not a good ethical rule. The purpose of this section is to explore the kinds of ethical
tests that Isabelle can carry out. In Section 3.2, I will explore Moshe Kroy's \cite{kroy} partial formalization of 
the first two formulations of the categorical imperative. I will also explore drawbacks of this attempt, 
particularly in the lack of the machinery to handle the important Kantian concept of a maxim: an action 
performed for a particular end. In Section 3.3, I will present my own improved
formalization of the categorical imperative.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Naive Formulation of the Formula of Universal Law%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
This section presents a simple and intuitive formalization of the formula of universal law, which 
is to will only those maxims that you would simultaneously will universalized. The universalizability 
test presents negative obligations: if a maxim passes the universalizability test, it is permissible. Else,
it is prohibited. In order to appropriately formalize this, we need some notion of permissibility.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ ddlpermissable{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t{\isasymRightarrow}t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}P{\isacharunderscore}{\isachardoublequoteclose}{\isacharparenright}\isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharparenleft}P\ A{\isacharparenright}\ {\isasymequiv}\ {\isacharparenleft}\isactrlbold {\isasymnot}{\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}A{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{An act $A$ is permissible if its negation is not obligated. For example, buying a red folder is 
permissible because I am not required to refrain from buying a red folder.%
}%
\begin{isamarkuptext}%
This naive formalization will require very little additional logical machinery, but more complex
formalizations may require additional logic concepts beyond just that of permissibility.

Let's now consider a naive reading of the Formula of Universal Law (FUL): `act only in accordance 
with that maxim through which you can at the same time will that it become a universal law' \cite{groundwork}.
An immediate translation to DDL is that if A is not necessary permissible then it is prohibited. In other
words, if we cannot universalize $P A$ (where universalizing is represented by the modal necessity 
operator), then $A$ is prohibited. Let's add this as an axiom to our logic.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{axiomatization}\isamarkupfalse%
\ \isakeyword{where}\isanewline
FUL{\isacharunderscore}{\isadigit{1}}{\isacharcolon}\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}{\isacharparenleft}\isactrlbold {\isasymnot}{\isacharparenleft}{\isasymbox}\ {\isacharparenleft}P\ A{\isacharparenright}{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}O\ {\isacharbraceleft}{\isacharparenleft}\isactrlbold {\isasymnot}A{\isacharparenright}{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%
\begin{isamarkuptext}%
Why add the categorical imperative as an axiom of this logic? The purpose of this logic is to 
perform ethical reasoning. Kant's ethical theory is rule based, so it involves applying the categorical
imperative to solve ethical dilemmas. In logic, this is equivalent to adopting the categorical imperative as 
an axiom and then reasoning in the newly formed logic to come to ethical conclusions. Adding the categorical
imperative as an axiom makes it impossible to violate it.

@@

 isn't necessarily obligated, it's not obligated anywhere. "%

@@

fact about murder (that it is wrong somewhere), so of course we were able to reach our desired conclusion.%

@@

\isamarkupcmt{Notice that this machinery is quite empty. We don't give an axioms about what a person can or can't do.%

@@

as represented by the universal quantifier in the first conjunct, and simulataneously \cite{simul}, as represented by 

@@

  Free variable:
    A = ($\lambda x. \_$)($i_1$ := False)\color{black}%
}\isanewline
%
\isamarkupcmt{This is exactly the desired result above - we have shown that models exist where an action can be 
neither obligatory nor prohibited.%
}\isanewline
%
\isamarkupcmt{Note that it's not clear \cite{kitcher} if Kant actually thought that permissibility was a coherent 
concept. Either way, in modern ethics, permissibility is a pretty widely accepted phenomenon.%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
Another initial test is the possibility of arbitrary obligations. If anything can be shown to be 
obligatory in this theory, then clearly it doesn't track out intuitions.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{lemma}\isamarkupfalse%
\ arbitrary{\isacharunderscore}obligations{\isacharcolon}\isanewline
\ \ \isakeyword{fixes}\ A{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t{\isachardoublequoteclose}\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}O\ {\isacharbraceleft}A{\isacharbraceright}\ w{\isachardoublequoteclose}\isanewline
\ \ \isacommand{nitpick}\isamarkupfalse%
\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharequal}true{\isacharbrackright}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
\isanewline
%
\isamarkupcmt{\color{blue} Nitpick found a counterexample for card i = 1:

  Free variable:
    A = ($\lambda x. \_$)($i_1$ := False) \color{black}%
}\isanewline
%
\isamarkupcmt{This is good! Shows us that any arbitrary term isn't obligatory.%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
$\textbf{Conflicting Obligations}$%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
A more complex metaethical property is the possibility of conflicting obligations. Many deontological
ethics are criticized for prescribing conflicting obligations, but it is clear that in Kantian ethics, 
obligations are never conflicting \cite{contradictoryob}. In order for morality to be action-guiding, it needs to be free of 
conflicting obligations. Let's see if we can have contradictary obligations under the naive formalization.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{lemma}\isamarkupfalse%
\ conflicting{\isacharunderscore}obligations{\isacharcolon}\isanewline
\ \ \isakeyword{fixes}\ A\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymand}\ O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ A{\isacharbraceright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
\ \ \isacommand{nitpick}\isamarkupfalse%
\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharequal}false{\isacharbrackright}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
\isanewline
%
\isamarkupcmt{\color{blue} Nitpick found a model for card i = 2:

@@

%:%41=14%:%
%:%42=15%:%
%:%43=16%:%
%:%52=18%:%

@@

%:%65=21%:%

@@

%:%67=23%:%
%:%69=25%:%
%:%70=25%:%
%:%71=26%:%
%:%73=27%:%
%:%74=28%:%

@@

%:%82=41%:%

@@

%:%84=43%:%
%:%86=45%:%

@@

@@

%:%99=57%:%
%:%100=58%:%

@@

%:%103=62%:%
%:%104=62%:%
%:%105=62%:%
%:%107=62%:%
%:%111=62%:%
%:%112=62%:%
%:%114=63%:%
%:%115=64%:%
%:%116=65%:%
%:%117=65%:%
%:%119=66%:%
%:%186=113%:%

@@

%:%199=116%:%

@@

%:%201=118%:%
%:%203=120%:%
%:%204=120%:%
%:%205=121%:%
%:%206=121%:%
%:%218=129%:%
%:%221=130%:%
%:%222=130%:%

@@

%:%225=132%:%
%:%226=133%:%
%:%227=134%:%
%:%228=134%:%
%:%229=135%:%
%:%230=136%:%
%:%231=136%:%
%:%232=137%:%
%:%233=138%:%
%:%236=139%:%
%:%240=139%:%
%:%241=139%:%
%:%242=139%:%
%:%244=140%:%
%:%245=141%:%
%:%255=143%:%
%:%256=144%:%
%:%257=145%:%
%:%261=147%:%
%:%263=149%:%
%:%264=149%:%
%:%265=150%:%
%:%266=150%:%
%:%267=151%:%
%:%268=151%:%
%:%270=152%:%
%:%271=152%:%
%:%272=153%:%
%:%273=154%:%

@@

@@

%:%277=157%:%

@@

%:%279=159%:%
%:%281=161%:%

@@

%:%283=162%:%
%:%284=163%:%
%:%285=164%:%
%:%286=164%:%
%:%289=165%:%
%:%293=165%:%
%:%294=165%:%

@@

%:%297=167%:%
%:%298=168%:%
%:%299=169%:%
%:%300=169%:%

@@

%:%304=172%:%
%:%305=173%:%
%:%306=174%:%
%:%307=174%:%
%:%309=175%:%
%:%310=176%:%

@@

%:%325=183%:%

@@

%:%327=185%:%
%:%329=187%:%

@@

%:%331=188%:%
%:%332=189%:%
%:%333=190%:%
%:%334=190%:%
%:%336=190%:%
%:%340=190%:%
%:%341=190%:%

@@

%:%346=194%:%
%:%347=195%:%
%:%348=196%:%

@@

%:%361=201%:%
%:%362=202%:%
%:%363=203%:%
%:%372=205%:%

@@

%:%393=216%:%

@@

%:%395=218%:%
%:%397=220%:%

@@

%:%399=221%:%
%:%400=222%:%
%:%401=223%:%
%:%402=223%:%
%:%404=223%:%
%:%408=223%:%
%:%409=223%:%

@@

%:%412=225%:%
%:%413=226%:%
%:%414=227%:%
%:%415=227%:%
%:%417=228%:%
%:%418=229%:%
%:%419=229%:%
%:%421=230%:%
%:%422=231%:%

@@

%:%433=234%:%
%:%435=236%:%

@@

%:%437=237%:%
%:%438=238%:%
%:%439=239%:%
%:%440=239%:%
%:%442=239%:%
%:%446=239%:%
%:%447=239%:%

@@

%:%450=241%:%
%:%451=242%:%
%:%452=243%:%
%:%453=243%:%
%:%455=244%:%
%:%465=246%:%

@@

%:%470=249%:%

@@

%:%472=251%:%
%:%474=253%:%

@@

%:%476=254%:%
%:%477=255%:%
%:%478=256%:%
%:%479=256%:%
%:%481=256%:%
%:%485=256%:%
%:%486=256%:%

@@

%:%489=258%:%
%:%490=259%:%
%:%491=260%:%
%:%492=260%:%
%:%494=261%:%
%:%504=263%:%

@@

%:%506=265%:%
%:%508=267%:%

@@

%:%510=268%:%
%:%511=269%:%
%:%512=270%:%
%:%513=270%:%
%:%515=270%:%
%:%519=270%:%
%:%520=270%:%
%:%522=271%:%
%:%523=272%:%
%:%524=273%:%
%:%525=273%:%
%:%527=274%:%
%:%537=276%:%

@@

%:%539=278%:%
%:%541=280%:%

@@

%:%545=283%:%
%:%546=284%:%
%:%547=285%:%
%:%548=285%:%
%:%555=286%:%
%:%556=286%:%
%:%557=287%:%
%:%558=287%:%
%:%559=288%:%
%:%560=288%:%
%:%561=289%:%
%:%562=289%:%
%:%563=289%:%
%:%564=289%:%
%:%566=290%:%
%:%567=291%:%
%:%568=291%:%
%:%569=292%:%
%:%570=292%:%
%:%571=292%:%

@@

%:%575=295%:%
%:%576=296%:%
%:%577=297%:%
%:%578=297%:%
%:%580=298%:%

@@

%:%592=302%:%

@@

%:%594=304%:%
%:%596=306%:%

@@

%:%598=307%:%
%:%599=308%:%
%:%600=309%:%
%:%601=309%:%
%:%603=309%:%
%:%607=309%:%
%:%608=309%:%

@@

%:%612=312%:%
%:%613=313%:%
%:%614=314%:%
%:%624=316%:%
%:%625=317%:%
%:%629=319%:%
%:%633=321%:%

@@

%:%635=323%:%
%:%637=325%:%
%:%638=325%:%
%:%639=326%:%
%:%642=327%:%
%:%646=327%:%
%:%647=327%:%
%:%649=328%:%
%:%650=328%:%

@@

%:%654=331%:%
%:%655=332%:%
%:%656=333%:%

@@

%:%667=336%:%

@@

%:%669=338%:%
%:%671=340%:%
%:%672=340%:%
%:%673=341%:%
%:%676=342%:%
%:%680=342%:%
%:%681=342%:%
%:%682=342%:%
%:%684=343%:%
%:%685=343%:%

>>>>

%
\begin{isabellebody}%
\setisabellecontext{paper{\isadigit{3}}{\isadigit{1}}}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{The Categorical Imperative%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
In this section, I will present two formulations of the categorical imperative. In Section \ref{sec:naive}, I will 
consider a simple, naive formulation of the formula of universal law. This formulation is, as I will 
show, clearly not a good ethical rule. The purpose of this section is to explore the kinds of ethical
tests that Isabelle can carry out. In Section \ref{sec:kroy}, I will explore Moshe Kroy's \cite{kroy} partial formalization of 
the first two formulations of the categorical imperative.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Naive Formulation of the Formula of Universal Law \label{sec:naive}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
This section presents a simple and intuitive formalization of the formula of universal law, which 
is to will only those maxims that you would simultaneously will universalized. The universalizability 
test creates negative obligations: if a maxim passes the universalizability test, it is permissible. Else,
it is prohibited. In order to appropriately formalize this, we need some notion of permissibility.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ ddlpermissable{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t{\isasymRightarrow}t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}P{\isacharunderscore}{\isachardoublequoteclose}{\isacharparenright}\isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharparenleft}P\ A{\isacharparenright}\ {\isasymequiv}\ {\isacharparenleft}\isactrlbold {\isasymnot}{\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}A{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{An act $A$ is permissible if its negation is not obligated. For example, buying a red folder is 
permissible because I am not required to refrain from buying a red folder.%
}%
\begin{isamarkuptext}%
This naive formalization will require very little additional logical machinery, but more complex
formalizations may require additional logic concepts.

Let's now consider a naive reading of the Formula of Universal Law (FUL): `act only in accordance 
with that maxim through which you can at the same time will that it become a universal law' \cite{groundwork}.
An immediate translation to DDL is that if $A$ is not necessary permissible then it is prohibited. In other
words, if we cannot universalize $P A$ (where universalizing is represented by the modal necessity 
operator), then $A$ is prohibited. Let's add this as an axiom to our logic.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{axiomatization}\isamarkupfalse%
\ \isakeyword{where}\isanewline
FUL{\isacharunderscore}{\isadigit{1}}{\isacharcolon}\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}{\isacharparenleft}\isactrlbold {\isasymnot}{\isacharparenleft}{\isasymbox}\ {\isacharparenleft}P\ A{\isacharparenright}{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}O\ {\isacharbraceleft}{\isacharparenleft}\isactrlbold {\isasymnot}A{\isacharparenright}{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%
\begin{isamarkuptext}%
Why add the categorical imperative as an axiom of this logic? The purpose of this logic is to 
perform ethical reasoning. Kant's ethical theory is rule based, so it involves applying the categorical
imperative to solve ethical dilemmas. In logic, this is equivalent to adopting the categorical imperative as 
an axiom and then reasoning in the newly formed logic to come to ethical conclusions. Adding the categorical
imperative as an axiom makes it impossible to violate it.

@@

 isn't necessarily obligated, it's not obligated anywhere.%

@@

fact about murder (that it is wrong somewhere), so it's not surprise that we were able to reach our desired conclusion.%

@@

\isamarkupcmt{Notice that this machinery is quite empty. We don't give axioms about what a person can or can't do.%

@@

as represented by the universal quantifier in the first conjunct, and simultaneously \cite{simul}, as represented by 

@@

  Free variable:
    A = ($\lambda x. \_$)($i_1$ := False)\color{black}%
}\isanewline
%
\isamarkupcmt{This is exactly the desired result above - we have shown that models exist where an action can be 
neither obligatory nor prohibited.%
}\isanewline
%
\isamarkupcmt{Note that it's not clear \cite{kitcher} if Kant actually thought that permissibility was a coherent 
concept. Either way, in modern ethics, permissibility is a pretty widely accepted phenomenon.%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
Another initial test is the possibility of arbitrary obligations. If anything can be shown to be 
obligatory in this theory, then clearly it doesn't track our intuitions.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{lemma}\isamarkupfalse%
\ arbitrary{\isacharunderscore}obligations{\isacharcolon}\isanewline
\ \ \isakeyword{fixes}\ A{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t{\isachardoublequoteclose}\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}O\ {\isacharbraceleft}A{\isacharbraceright}\ w{\isachardoublequoteclose}\isanewline
\ \ \isacommand{nitpick}\isamarkupfalse%
\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharequal}true{\isacharbrackright}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
\isanewline
%
\isamarkupcmt{\color{blue} Nitpick found a counterexample for card i = 1:

  Free variable:
    A = ($\lambda x. \_$)($i_1$ := False) \color{black}%
}\isanewline
%
\isamarkupcmt{This is good! Shows us that any arbitrary term isn't obligatory.%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
$\textbf{Conflicting Obligations}$%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
A more complex metaethical property is the possibility of conflicting obligations. Many deontological
ethics are criticized for prescribing conflicting obligations, but in Kantian ethics, 
obligations never conflict \cite{contradictoryob}. In order for morality to be action-guiding, it needs to be free of 
conflicting obligations. Let's see if we can have contradictary obligations under the naive formalization.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{lemma}\isamarkupfalse%
\ conflicting{\isacharunderscore}obligations{\isacharcolon}\isanewline
\ \ \isakeyword{fixes}\ A\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymand}\ O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ A{\isacharbraceright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
\ \ \isacommand{nitpick}\isamarkupfalse%
\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharequal}false{\isacharbrackright}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
\isanewline
%
\isamarkupcmt{\color{blue} Nitpick found a model for card i = 2:

@@

%:%49=15%:%
%:%61=17%:%
%:%62=18%:%
%:%63=19%:%

@@

@@

%:%67=22%:%
%:%68=23%:%
%:%70=24%:%
%:%71=25%:%
%:%74=33%:%
%:%75=34%:%
%:%76=35%:%

@@

@@

%:%84=42%:%
%:%85=43%:%

@@

%:%89=47%:%

@@

%:%100=59%:%

@@

%:%102=59%:%
%:%104=59%:%
%:%108=59%:%
%:%109=59%:%
%:%111=60%:%
%:%112=61%:%
%:%113=62%:%
%:%114=62%:%
%:%116=63%:%
%:%183=110%:%
%:%195=112%:%
%:%196=113%:%
%:%197=114%:%

@@

@@

%:%201=117%:%
%:%202=118%:%
%:%203=118%:%
%:%215=126%:%
%:%218=127%:%
%:%219=127%:%
%:%221=128%:%
%:%222=129%:%
%:%223=130%:%

@@

%:%225=131%:%
%:%226=132%:%
%:%227=133%:%
%:%228=133%:%
%:%229=134%:%
%:%230=135%:%
%:%233=136%:%
%:%237=136%:%
%:%238=136%:%
%:%239=136%:%
%:%241=137%:%
%:%242=138%:%
%:%252=140%:%
%:%253=141%:%
%:%254=142%:%
%:%258=144%:%
%:%260=146%:%
%:%261=146%:%
%:%262=147%:%
%:%263=147%:%
%:%264=148%:%
%:%265=148%:%
%:%267=149%:%
%:%268=149%:%
%:%269=150%:%
%:%270=151%:%
%:%271=151%:%
%:%273=153%:%

@@

%:%275=155%:%

@@

@@

%:%279=158%:%
%:%280=159%:%
%:%281=160%:%

@@

%:%283=161%:%
%:%286=162%:%
%:%290=162%:%
%:%291=162%:%
%:%293=163%:%
%:%294=164%:%
%:%295=165%:%

@@

%:%297=166%:%
%:%299=167%:%
%:%300=168%:%
%:%301=169%:%

@@

%:%304=171%:%
%:%306=172%:%
%:%307=173%:%
%:%317=175%:%
%:%318=176%:%
%:%319=177%:%

@@

@@

%:%327=184%:%
%:%328=185%:%
%:%329=186%:%

@@

%:%331=187%:%
%:%333=187%:%
%:%337=187%:%
%:%338=187%:%
%:%340=188%:%
%:%341=189%:%
%:%342=190%:%

@@

%:%355=195%:%
%:%356=196%:%
%:%357=197%:%

@@

%:%369=202%:%
%:%381=204%:%
%:%382=205%:%
%:%383=206%:%

@@

@@

%:%395=217%:%
%:%396=218%:%
%:%397=219%:%

@@

%:%399=220%:%
%:%401=220%:%
%:%405=220%:%
%:%406=220%:%
%:%408=221%:%
%:%409=222%:%
%:%410=223%:%

@@

%:%412=224%:%
%:%414=225%:%
%:%415=226%:%
%:%416=226%:%
%:%418=227%:%
%:%419=228%:%
%:%429=230%:%
%:%430=231%:%

@@

%:%433=233%:%
%:%434=234%:%
%:%435=235%:%

@@

%:%437=236%:%
%:%439=236%:%
%:%443=236%:%
%:%444=236%:%
%:%446=237%:%
%:%447=238%:%
%:%448=239%:%

@@

%:%450=240%:%
%:%452=241%:%
%:%462=243%:%
%:%466=245%:%
%:%467=246%:%
%:%468=247%:%

@@

@@

%:%472=250%:%
%:%473=251%:%
%:%474=252%:%

@@

%:%476=253%:%
%:%478=253%:%
%:%482=253%:%
%:%483=253%:%
%:%485=254%:%
%:%486=255%:%
%:%487=256%:%

@@

%:%489=257%:%
%:%491=258%:%
%:%501=260%:%
%:%502=261%:%
%:%503=262%:%

@@

%:%506=264%:%
%:%507=265%:%
%:%508=266%:%

@@

%:%510=267%:%
%:%512=267%:%
%:%516=267%:%
%:%517=267%:%
%:%519=268%:%
%:%520=269%:%
%:%521=270%:%
%:%522=270%:%
%:%524=271%:%
%:%534=273%:%
%:%535=274%:%
%:%536=275%:%

@@

%:%539=277%:%
%:%540=278%:%
%:%541=279%:%

@@

%:%545=282%:%
%:%552=283%:%
%:%553=283%:%
%:%554=284%:%
%:%555=284%:%
%:%556=285%:%
%:%557=285%:%
%:%558=286%:%
%:%559=286%:%
%:%560=286%:%
%:%561=286%:%
%:%563=287%:%
%:%564=288%:%
%:%565=288%:%
%:%566=289%:%
%:%567=289%:%
%:%568=289%:%
%:%570=290%:%
%:%571=291%:%
%:%572=292%:%

@@

%:%575=294%:%
%:%577=295%:%
%:%587=297%:%
%:%588=298%:%
%:%589=299%:%

@@

@@

%:%594=303%:%
%:%595=304%:%
%:%596=305%:%

@@

%:%598=306%:%
%:%600=306%:%
%:%604=306%:%
%:%605=306%:%
%:%607=307%:%
%:%608=308%:%
%:%609=309%:%

@@

%:%621=313%:%
%:%622=314%:%
%:%626=316%:%
%:%630=318%:%
%:%631=319%:%
%:%632=320%:%

@@

%:%635=322%:%
%:%636=323%:%
%:%639=324%:%
%:%643=324%:%
%:%644=324%:%
%:%646=325%:%
%:%647=325%:%
%:%649=326%:%
%:%650=327%:%
%:%651=328%:%

@@

%:%663=332%:%
%:%664=333%:%
%:%665=334%:%

@@

@@

%:%669=337%:%
%:%670=338%:%
%:%673=339%:%
%:%677=339%:%
%:%678=339%:%
%:%679=339%:%
%:%681=340%:%
%:%682=340%:%
